---
title: "Week6_midterm1"
author: "Yunting"
date: "2/21/2020"
output: pdf_document
---
# Question 1: Star Wars Characters
#### The starwars data frame in the dplyr package contains demographic characteristics of various characters from the hit franchise Star Wars. We will use this data frame for question 1.

## 1.
```{r}
library(tidyverse)
library(dplyr)
head(starwars)
tail(starwars)
```

##  2. 
```{r}
starwars %>%
  filter(is.na(gender)) %>%
 select(name,height,species,gender) %>%
  arrange(height)
  

```

## 3.
```{r}
starwars %>%
  filter(is.na(gender)) %>%
 select(name,height,species,gender) %>%
 arrange(height) %>%
  mutate(gender = "droid") %>%
  
 head()

```

## 4. 
```{r}
starwars %>%
   mutate(BMI = (mass/(height/100)^2))%>%
           head()
  
  
  
```

## 5.
```{r}
starwars %>%
 group_by(gender) %>%
  summarize(Max_height = max(height, na.rm = TRUE), Min_height = min(height, na.rm = TRUE), number = n())

  
  
```

## 6. 
```{r}
starwars %>%
   mutate(BMI = (mass/sqrt(height/100)))%>%
  filter(gender == "male" | gender == "female" | is.na(gender)) %>%
  
ggplot(aes(x = gender, y = BMI, fill = gender)) +
  theme_bw() +
  geom_boxplot()



  
  
```

## 7. 
```{r}
starwars %>%
  ggplot(aes(x = height, y = mass, fill = hair_color )) +
  theme_bw() +
  geom_point()
  
```

## 8.
```{r}
starwars %>%
   filter(gender == "male" | gender == "female" | gender == "none" |  is.na(gender)) %>%
  filter(birth_year < 120) %>%
  ggplot(aes(x = birth_year, y = height, color = gender)) +
    theme_bw() +
    ggtitle("Height by Birth Year and Gender") +
  geom_point() +
  xlab("Birth Year") +
  ylab("Height") +
  geom_smooth( se = FALSE, linetype = "dashed", color = "black")
  
  
```

# Question 2: Coding Exercises
## 1. 
```{r}
convert <- function(x){
  stopifnot(is.numeric(x))
  
  if(x %% 2 ==0){return(x^2)
  }else if (x %% 2 ==1){return(x^3)
  }else if(!(is.integer(x))){
        return(Inf)}
  
  
  
  
  
  
}

convert(0)
convert(4)
convert(7)
convert(2.5)
```

## 2. (4 pts) Reproduce the following lines (with URL) and table in R Markdown:

* Typing Test Phrases

--*The* **quick** [brown](https://r4ds.had.co.nz/) ~~fox~~ jumps

 over | the
 -----|-------
 lazy | dog

* Math Phrases

 -- – Given a sample of size n from a population with values $y_{i}$, we use $\overline{Y}$ to estimate the true mean $\mu$ where $$\overline{Y} = \sum_{i=1}^{n} \frac{y_{i}}{n}$$



## 3.
```{r error=TRUE}
set.seed(1)
Test123 <-  function(a){
  stopifnot(length(a) <= 5)} %>%
  
  
  ggplot(Test123, mapping = aes(x = rnorm(1000, mean = a, sd = 1)))+
  geom_histogram(bins = 50,fill = "white", color = "blue")+
  theme_minimal()+
  xlab("x")

Test123(c(1,-10.2,5))
Test123(c(1,2,3,4,5,6))
```

